Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Enhanced Flexibility

### 2024-11-19 main.tex
:construction: Add corollary 3.5

% enumitem
\setlist[itemize]{leftmargin=5mm}
\setlist[enumerate]{leftmargin=5mm}

@@

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{ao}{AO}{Alternating Optimization}
\newacronym{bd}{BD}{Beyond Diagonal}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{d}{D}{Diagonal}
\newacronym{dof}{DoF}{Degrees of Freedom}
\newacronym{siso}{SISO}{Single-Input Single-Output}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{pc}{PC}{Point-to-point Channel}
\newacronym{ic}{IC}{Interference Channel}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{wsr}{WSR}{Weighted Sum-Rate}
\newacronym{svd}{SVD}{Singular Value Decomposition}
\newacronym{mmse}{MMSE}{Minimum Mean-Square Error}
\newacronym{wmmse}{WMMSE}{Weighted \gls{mmse}}
\newacronym{mse}{MSE}{Mean-Square Error}
\newacronym{los}{LoS}{Line-of-Sight}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{sca}{SCA}{Successive Convex Approximation}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}

@@

	\begin{example}[\gls{siso} channel gain maximization]\label{eg:siso_gain}
		Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
		In this case, mode alignment boils down to phase matching and any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using
		% the scattering matrix maximizing the channel gain is
		\begin{equation}
			\mathbf{\Theta}_g^\textnormal{\gls{siso}} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
			\label{eq:scattering_siso}
		\end{equation}
		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g} \in \mathbb{C}^{1 \times L}$, respectively.
		The corresponding channel gain is a function of $L$
		% Here any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect mode alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using \eqref{eq:scattering_siso}.
		% However, the branch matching capability is a function of $L$ and the channel gain can be manipulated
		\begin{equation}
			\lvert h \rvert _{\max} = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
			\label{eq:gain_siso}
		\end{equation}
		where $h_{\mathrm{B},g,l}$, $h_{\mathrm{F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively, and $\pi_{\mathrm{B},g}$, $\pi_{\mathrm{F},g}$ are permutations of $[L]$ sorting their magnitude in non-ascending orders.
		That is, the maximum channel gain is attained when each group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
		A larger $L$ provides better branch matching flexibility and can thus grant a higher channel gain.
		% It is evident that the branch matching capability increases with $L$.
		% the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
		% The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.
	\end{example}

@@

		Proposition \ref{pp:direct_negligible} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
		Its importance lies in the fact that the channel shaping question in Section \ref{sc:contributions} can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
		The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} over the notation\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
		% $N < n \le \bar{N}$.
		These results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
		% We have the following corollaries.

		\begin{corollary}[Product of subset of singular values\label{co:sv_bound_horn}]
			The product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
			\begin{equation}
				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
				\label{iq:sv_bound_fc}
			\end{equation}
			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
			\begin{equation*}
				\begin{split}
					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} & \bigm\vert \forall p < r, \ \forall (F, G, H) \in T_p^r,\\
					& \quad \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
				\end{split}
			\end{equation*}
			\begin{equation*}
				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \subseteq [\bar{N}]^3 \bigm\vert \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + \frac{r(r+1)}{2}\Bigr\}.
			\end{equation*}
		\end{corollary}

@@

		Corollary \ref{co:sv_bound_horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result under the assumption of Proposition \ref{pp:direct_negligible} (i.e., negligible direct channel and fully-connected \gls{bd}-\gls{ris}).
		% It is worth mentioning that t
		% It also helps to induce lower bounds on the channel singular values.
		The number of admissible triples increases exponentially with $\bar{N}$ despite some resulting inequalities can be redundant.
		Apart from upper bounds, \eqref{iq:sv_bound_fc} can also induce lower bounds on channel singular values.
		% It also helps to induce lower (instead of upper) bounds on channel singular values.
		% ! For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
		% Besides, \eqref{iq:sv_bound_fc} helps to induce lower bounds
		Those facts render the shaping limit analysis non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
		Below we showcase some useful results that can be derived from Corollary \ref{co:sv_bound_horn}.

		\begin{corollary}[Product of some largest or smallest singular values\label{co:sv_product}]
			% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
			% For any $k \in [\bar{N}]$,
			The product of the first (resp. last) $k$ singular values of $\mathbf{H}$ is bounded from above (resp. below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
			% the product of the first (resp. last) $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
			% upper bounded by the product of first and last $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
			% $k$ singular values of $\mathbf{H}$ can be upper bounded by the product of first $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
			\begin{subequations}
				\begin{align}
					\prod_{n=1}^k \sigma_n(\mathbf{H}) & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_product_largest} \\
					\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:sv_product_smallest}
				\end{align}
			\end{subequations}
		\end{corollary}

		\begin{proof}
			Please refer to and Appendix~\ref{ap:sv_product}.
		\end{proof}

>>>>

% enumitem
\setlist[itemize]{leftmargin=4mm}
\setlist[enumerate]{leftmargin=4mm}

@@

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{ao}{AO}{Alternating Optimization}
\newacronym{bd}{BD}{Beyond Diagonal}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{d}{D}{Diagonal}
\newacronym{dof}{DoF}{Degrees of Freedom}
\newacronym{siso}{SISO}{Single-Input Single-Output}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{pc}{PC}{Point-to-point Channel}
\newacronym{ic}{IC}{Interference Channel}
\newacronym{wsr}{WSR}{Weighted Sum-Rate}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{svd}{SVD}{Singular Value Decomposition}
\newacronym{mmse}{MMSE}{Minimum Mean-Square Error}
\newacronym{wmmse}{WMMSE}{Weighted \gls{mmse}}
\newacronym{mse}{MSE}{Mean-Square Error}
\newacronym{los}{LoS}{Line-of-Sight}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{sca}{SCA}{Successive Convex Approximation}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}

@@

	\begin{example}[\gls{siso} channel gain maximization]\label{eg:siso_gain}
		Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
		In this case, mode alignment boils down to phase matching and any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using
		% the scattering matrix maximizing the channel gain is
		\begin{equation}
			\mathbf{\Theta}_g^\textnormal{\gls{siso}} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
			\label{eq:scattering_siso}
		\end{equation}
		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g} \in \mathbb{C}^{1 \times L}$, respectively.
		The corresponding channel gain is a function of $L$
		% Here any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect mode alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using \eqref{eq:scattering_siso}.
		% However, the branch matching capability is a function of $L$ and the channel gain can be manipulated
		\begin{equation}
			\lvert h \rvert _{\max} = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
			\label{eq:gain_siso}
		\end{equation}
		where $h_{\mathrm{B},g,l}$, $h_{\mathrm{F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively, and $\pi_{\mathrm{B},g}$, $\pi_{\mathrm{F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
		That is, the maximum channel gain is attained when each group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
		A larger $L$ provides better branch matching flexibility and can thus grant a higher channel gain.
		% It is evident that the branch matching capability increases with $L$.
		% the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
		% The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.
	\end{example}

@@

		Proposition \ref{pp:direct_negligible} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
		Its importance lies in the fact that the channel shaping question in Section \ref{sc:contributions} can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
		The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sv_nth} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
		% define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
		% where we assume $N \le N_\mathrm{S}$ for the ease of notation and define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N_\mathrm{S}] \setminus [N]$.
		% \footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $N = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N] \setminus [N]$}.
		% over the notation\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $N = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N] \setminus [N]$.
		% $N < n \le N$.
		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
		% We have the following corollaries.

		\begin{corollary}[Product of subset of singular values\label{co:sv_bound_horn}]
			If the direct channel is negligible,
			% and $N \le N_\mathrm{S}$
			then the product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
			\begin{equation}
				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
				\label{iq:sv_bound_fc}
			\end{equation}
			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
			\begin{equation*}
				\begin{split}
					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \bigm\vert & \forall p < r, \ \forall (F, G, H) \in T_p^r,\\
					& \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
				\end{split}
			\end{equation*}
			\begin{equation*}
				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \subseteq [\bar{N}]^3 \bigm\vert \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + \frac{r(r+1)}{2}\Bigr\}.
			\end{equation*}
		\end{corollary}

@@

		\eqref{iq:sv_bound_fc}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:direct_negligible}.
		% It is worth mentioning that t
		% It also helps to induce lower bounds on the channel singular values.
		The number of admissible triples increases exponentially with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
		Apart from the upper bounds, we will shortly see \eqref{iq:sv_bound_fc} can also induce lower bounds on channel singular values.
		% It also helps to induce lower (instead of upper) bounds on channel singular values.
		% ! For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.
		% Besides, \eqref{iq:sv_bound_fc} helps to induce lower bounds
		Those facts render the analysis of shaping limit non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
		Below we showcase some useful resulting bounds.

		\begin{corollary}[Product of some largest or smallest singular values\label{co:sv_product}]
			% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
			% For any $k \in [N]$,
			If the direct channel is negligible,
			% and $N \le N_\mathrm{S}$
			then the product of the first (resp. last\footnote{The lower bounds coincide at zero when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp. below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
			% the product of the first (resp. last) $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
			% upper bounded by the product of first and last $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
			% $k$ singular values of $\mathbf{H}$ can be upper bounded by the product of first $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
			\begin{subequations}
				\begin{align}
					\prod_{n=1}^k \sigma_n(\mathbf{H}) & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_product_largest} \\
					\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:sv_product_smallest}
				\end{align}
			\end{subequations}
		\end{corollary}

		\begin{proof}
			Please refer to Appendix~\ref{ap:sv_product}.
		\end{proof}

		% The assumption $N \le N_\mathrm{S}$

		\begin{corollary}[Individual singular value\label{co:sv_nth}]
			If the direct channel is negligible,
			% and $N \le N_\mathrm{S}$,
			then the $n$-th channel singular value can be manipulated up to
			\begin{equation}
				\max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
				\label{iq:sv_nth}
			\end{equation}
			where $(i, j) \in [N_\mathrm{S}]^2$.
			The upper and lower bounds are attained respectively at
			\begin{subequations}
				\label{eq:sv_nth}
				\begin{align}
					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
				\end{align}
			\end{subequations}
			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are the right and left singular matrices\footnote{We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$. When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace. Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.} of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
			and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary permutation matrices of dimension $N_\mathrm{S}$ satisfying:
			\begin{itemize}
				\item The $(i, j)$-th entry is $1$, where
				% \begin{equation*}
				% 	(i, j) =
				% 	\begin{cases}
				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
				% 		\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
				% 	\end{cases}
				% \end{equation*}
				\begin{subnumcases}{(i, j) =}
					\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:sv_nth_max_pair} \\
					\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
				\end{subnumcases}
				% \begin{equation*}
				% 	(i, j) =
				% 	\begin{cases}
				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
				% 		\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
				% 	\end{cases}
				% \end{equation*}
				and ties may be broken arbitrarily;
				% with ties broken arbitrarily;
				% and the tie-breaking rule is arbitrary.
				\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
				% \begin{subequations}
				% 	\begin{alignat}{1}
				% 		\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{P}, \hspace{-0.17cm} \label{eq:sv_nth_max_condition} \\
				% 		\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{Q}, \hspace{-0.17cm} \label{eq:sv_nth_min_condition}
				% 	\end{alignat}
				% \end{subequations}

				\begin{subequations}
					\begin{alignat}{2}
						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{P}, \label{eq:sv_nth_max_condition} \\
						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
					\end{alignat}
				\end{subequations}
				% \begin{subequations}
				% 	\begin{align}
				% 		\sigma_{n-1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \ge \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{P}, \label{eq:sv_nth_max_condition} \MoveEqLeft[1] \\
				% 		\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
				% 	\end{align}
				% \end{subequations}
				where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
			\end{itemize}
		\end{corollary}
